Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
...

@@

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or neurons.

@@

	\begin{align}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e}
	\end{align}

@@

	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct neuron that should be activated, $v$ the other type of neurons.

@@

	%gamma = infini meilleur sur une itération

	$P(n_{v_c} = x + \gamma ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$

	$P(n_{v_c} = x) = {a c_k \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e) - x }$

	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$.

	$P(n_v = x) = {a c_k \choose x} P_+^x (1-P_+)^{a c_k -x }$

	% À corriger avec sommes multiparties
	$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$

	% Approx : ?! $P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

>>>>

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

@@

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or neurons. Messages are considered independent and identically distributed.

@@

	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{agc} = n)^k P(n_{agc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{be} < n)^{l-2a} P(n_{abe} < n)^a \right ]^{c_e} \numberthis \label{from_err_th}
	\end{align*}

@@

	As information is shared across connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct neuron that should be activated, $v$ the other type of neurons.

@@

	%gamma = infini meilleur sur une itération
	With probability $1 - \psi$, the correct vertex is still connected to a given activated neuron in an intact cluster. Thus $P(n_{v_c} = x ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$

	%$P(n_{v_c} = x) = {a c_k \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e) - x }$

	The probability for an edge to be present in the network after damages is : $P_+ = \psi (1 - d) + (1 - \psi) d$. So for other neurons $P(n_v = x) = {a (c - c_e) \choose x} P_+^x (1-P_+)^{a (c - c_e) -x }$.

	% À corriger avec sommes multiparties
%	$P(\mbox{no other vertex activated in this cluster})= \sum_{n_0 = 1}^{a (c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a}$
%	
	% Approx : ?! $P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n_0 = 1}^{a ( c - c_e)} P(n_{v_c} \ge n_0)^a \left [ \sum_{x = 0}^{n_0 - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$
